Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Wording of "Problem summary"

Here is a summary of the problem:

\begin{itemize}
\item
    For user documentation,
    Haddock does not have markup to describe evidence.
\item
    For code documentation,
    Hspec does not provide combinators to express expectations with
    BDD terminology.
\item
    Automatic discovery for specs is missing (TBD)
\end{itemize}

>>>>

Here is a summary of the problems:

\begin{itemize}
\item
    There is no way to automatically test examples and properties
    contained in user documentation.
\item
    For code documentation,
    Hspec does not provide combinators to express expectations in
    BDD terminology.
\item
    There is no facility that automatically finds and combines all
    specs of a project.
\end{itemize}
